Supplement

### 2023-06-30 code/process.Rmd
fixes based on meeting with Maya

```
Descriptions:

- "done" -- fully coded, can be used for whatever is specified in other column 
- "cannot tell direction" -- have stats for an effect, but can't tell which direction it is in
- "unusable" -- got as far as I can, and it does not have complete descriptives
- "missing" -- student didn't finish or we don't have write-up
- "non-experiment" -- student replicated something that was not an experiment
- "reproduction" -- student did a reproduction and not replication

@@

test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |> select(target_lastauthor_year, target_raw_stat)

test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> select(target_lastauthor_year, replication_raw_stat)

@@

d_es_predInt <- d_es |> 
  rowwise() |> 
  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
         sub_rep = do_subjective_rep(replicated_instructor_code, 
                                     replicated_report_code, 
                                     adjudicated_replication_code)) |> write_csv(here("data","processed_data.csv"))
```

# viz SMD

@@

# how close subrep

@@

@@

Note: tier 2 and 3 models are subject to change as a few more studies might in fact have useable stats & some of the effect size extraction might be incorrect.

@@

## Frequentist Lassoes

@@

### Pred_int
Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!

@@

### P_orig
Note: predInt may not be reliably calculated in some cases. Dealing with numbers is hard!

>>>>

@@

test |> filter(is.na(target_ES)&(is.na(target_d_calc))) |> filter(!is.na(target_raw_stat)) |> select(target_lastauthor_year, target_raw_stat)

test |> filter(is.na(rep_ES)&(is.na(rep_d_calc))) |> filter(!is.na(replication_raw_stat)) |> select(target_lastauthor_year, replication_raw_stat)

@@

#d_es |> filter(is.na(target_ES)!=is.na(target_SE))
#d_es |> filter(is.na(rep_ES)!=is.na(rep_SE))
#d_es |> filter(is.na(rep_d_calc)!=is.na(rep_d_calc_se)) #fine all of the bad ones are exp only
#d_es |> filter(is.na(target_d_calc)!=is.na(target_d_calc_se))

d_es_predInt <- d_es |> 
  rowwise() |> 
  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE), # on untransformed scale
         predInt_from_d = do_pred_int(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se), #on standardized scale 
         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
         p_orig_from_d = do_p_orig(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se),
         predInt=ifelse(is.na(predInt), predInt_from_d, predInt), #prefer untransformed scale, but use standardized when that's the only option
         p_orig=ifelse(is.na(p_orig), p_orig_from_d, p_orig), # prefer untrasformed when available 
         predInt_with_tau = do_pred_int_sens(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se), #on standardized scale 
         p_orig_with_tau = do_p_orig_sens(target_d_calc, target_d_calc_se, rep_d_calc, rep_d_calc_se),
         sub_rep = do_subjective_rep(replicated_instructor_code, 
                                     replicated_report_code, 
                                     adjudicated_replication_code)) |> write_csv(here("data","processed_data.csv"))

#d_es_predInt |> filter(include!="exp") |> filter(is.na(predInt))
#d_es_predInt |> filter(include!="exp") |> filter(is.na(p_orig))

<!-- # viz SMD

@@

<!-- # how close subrep

@@

```
-->

@@

@@

<!-- 
## Frequentist Lassoes
Note these have not been updated since corrections to data pipeline 
```{r}

@@

### Pred_int

@@

### P_orig

### 2023-06-30 paper/manuscript.tex
fixes based on meeting with Maya

Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate. 45\% (61/136) of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication. This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).

@@

Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (0.55, CrI= {[}-0.01, 2{]}). In the model with all predictors, but less data, within-subjects designs remain predictive (0.64, CrI= {[}-0.03, 2.38{]}), and standardized effect size is also a strong predictor of subjective replication score (0.59, CrI= {[}0.31, 2.58{]}). Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.34{]}; effect size 0.97, CrI= {[}0.76, 4.59{]}).

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models. The strongest predictors for prediction interval were still within-subjects designs (0.71, CrI= {[}-0.12, 2.38{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.31, 0.89{]}).

>>>>

Across the 176 studies, the average subjective replication score was 49\%, which we can interpret as an overall subjective replication rate. 46\% (62/136) of the studies had replication outcomes within the prediction interval of the original outcome. The median p\_original value was 0.03 representing the median probability that a replication study's estimate would be at least as extreme as was actually observed, if in fact the replication and original were statistically consistent. Figure \ref{fig:smd} shows the relationship between original standardized effect size, replication effect size, and subjective replication score. Some studies replicated withed similar size effects to the original, and others failed to replicate, with replication effect sizes near zero. On average, there was a diminution of effect sizes from original to replication. This pattern of results is consistent with the pattern of results found in RP:P (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}).

@@

Within-subjects designs stand out as the strongest indicator of replicability in the model with all the data (0.53, CrI= {[}0, 2{]}). In the model with all predictors, but less data, within-subjects designs remain predictive (0.66, CrI= {[}-0.04, 2.37{]}), and standardized effect size is also a strong predictor of subjective replication score (0.65, CrI= {[}0.27, 2.81{]}). Both effects are robust to a sensitivity analysis including only studies with close replications and matching statistical tests (within-subjects 0.87, CrI= {[}-0.01, 3.33{]}; effect size 1.05, CrI= {[}0.76, 4.88{]}).

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models. The strongest predictors for prediction interval were still within-subjects designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).

### 2023-06-30 paper/supplement.Rmd
fixes based on meeting with Maya

```{r, include=F, echo=F}
library(Replicate)
do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
  }
  return(NA)
}

do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
    yio=target_ES
    vio=target_SE**2
    yir=rep_ES
    vir=rep_SE**2
    t2=.21**2
    pooled.SE = sqrt(vio + vir + t2)
    PILo.sens = yio - qnorm(0.975) * pooled.SE
    PIHi.sens = yio + qnorm(0.975) * pooled.SE
    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
    return(PIinside.sens)
  }
  return(NA)
}
do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
  }
  return(NA)
}

do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21**2, rep_SE**2))
  }
  return(NA)
}
check_sens <- d |> filter(include=="stats") |>
  mutate(sens_target_d=target_d_calc,
         sens_target_se=target_SE*target_d_calc/target_ES,
         sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
         sens_rep_d=rep_d_calc,
         sens_rep_se=rep_SE*rep_d_calc/rep_ES,
         sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |>

  rowwise() |>
  mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
         p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
         predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
         p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))

check_sens |> select(starts_with("sens"))
check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |>
  filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()

check_sens |> group_by(predIntSens) |> tally()
check_sens |> group_by(predInt2) |> tally()
check_sens |> group_by(predInt) |> tally()

check_sens |> ungroup() |> summarize(m=median(p_origSens))
check_sens |> ungroup() |> summarize(m=median(p_orig2))
check_sens |> ungroup() |> summarize(m=median(p_orig))

check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)

d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
```

>>>>

```{r, include=F, echo=F}
d |> select(starts_with("pred") | starts_with("p_orig"))

d |> filter(!is.na(predInt)) |> count(predInt)
#using predInt as reported 62 in interval, 72 not (45% rep)

#of those with SMD predInts
d |> filter(!is.na(predInt_from_d)) |> count(predInt)
# using predInt 44 in / 70 out (38%)
d |> filter(!is.na(predInt_from_d)) |> count(predInt_from_d)
# 34 in /80 out (30%)
d |> filter(!is.na(predInt_from_d)) |> count(predInt_with_tau)
# with tau 73 in / 41 out (64%)

d |> filter(!is.na(predInt)) |> summarise(median(p_orig))
#median .03

#of those with SMD predInts
d |> filter(!is.na(predInt_from_d)) |>summarise(median(p_orig))
# median .01
d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_from_d))
# median .001
d |> filter(!is.na(predInt_from_d)) |> summarise(median(p_orig_with_tau))
# median .15
```
